\section{Research Questions: Paper}
\begin{frame}
    \begin{enumerate}
        \item \textbf{RQ1 Storage}: What do existing distributed social networks use for storage of the distributed ledger (DLT)?
        \begin{enumerate}
            \item \textbf{Methodology}: Evaluate existing projects from legacy p2p systems to modern distributed networks and blockchains.
            \item \textbf{Goal}: Build an argument for using a specific data structure, based on an iterative interaction analysis, from storing elementary p2p relations to complex interactions as feed building.
        \end{enumerate}
        \item \textbf{RQ2 Consensus}: What type of consensus is needed for distributed social networks?
        \begin{enumerate}
            \item \textbf{Methodology}: Analyze current consensus methods and explore cheaper alternatives to the classic 50\% + 1 vote.
            \item \textbf{Goal}: Build an argument for using a specific consensus algorithm (e.g., PoW, PoS, PoA, (p)BFT, Raft, Paxos).
        \end{enumerate}
        \item \textbf{RQ3 Communication}: How are messages broadcast in a distributed network?
        \begin{enumerate}
            \item \textbf{Methodology}: Investigate the efficiency of traditional p2p unicast communication and explore multipoint communication alternatives.
            \item \textbf{Goal}: Enhance network resilience to faults and improve efficiency in terms of latency, storage, and bandwidth.
        \end{enumerate}
    \end{enumerate}
\end{frame}